### 2021-04-28 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

\documentclass[11pt]{proposalnsf}
\usepackage{times}
\usepackage{mathptmx}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{array}
\usepackage[noend,nofillcomment]{algorithm2e}
\usepackage{verbatim}
%\usepackage{algorithmic}
%\usepackage{amsfonts}
%\usepackage{lineno}
\usepackage{ifthen}
\usepackage{booktabs}

\usepackage{color}

\usepackage{multirow}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

\makeatletter
\def\tightitemize{\ifnum \@itemdepth >3 \@toodeep\else \advance\@itemdepth \@ne
\edef\@itemitem{labelitem\romannumeral\the\@itemdepth}%
\list{\csname\@itemitem\endcsname}{\setlength{\topsep}{-\parskip}\setlength{\parsep}{0in}\setlength{\itemsep}{0in}\setlength{\parskip}{0in}\def\makelabel##1{\hss\llap{##1}}}\fi}
\let\endtightitemize =\endlist
\def\tightenumerate{%
\ifnum \@enumdepth >\thr@@\@toodeep\else
\advance\@enumdepth\@ne
\edef\@enumctr{enum\romannumeral\the\@enumdepth}%
\expandafter
\list
\csname label\@enumctr\endcsname
{\setlength{\topsep}{-\parskip}\setlength{\parsep}{0in}\setlength{\itemsep}{0in}\setlength{\parskip}{0in}\usecounter\@enumctr\def\makelabel##1{\hss\llap{##1}}}%
\fi}
\let\endtightenumerate =\endlist
\makeatother
\renewcommand{\refname}{\centerline{References cited}}

% this handles hanging indents for publications
\def\rrr#1\\{\par
\medskip\hbox{\vbox{\parindent=2em\hsize=6.12in
\hangindent=4em\hangafter=1#1}}}

\def\baselinestretch{1}

\begin{document}

\begin{center}
{\Large{\bf VLDB 2021 - Notes for Reviewers}}

\end{center}

Here we address rebviews comments 1 by one.

\newpage
\pagenumbering{arabic}

\end{document}

### 2021-04-28 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

% this handles hanging indents for publications
\def\rrr#1\\{\par
\medskip\hbox{\vbox{\parindent=2em\hsize=6.12in
\hangindent=4em\hangafter=1#1}}}

\def\baselinestretch{1}

\begin{document}

\begin{center}
{\Large{\bf VLDB 2021 - Response to Reviews: \\
Using VDMS to Index and Search 100M Images}}

@@

\end{center}

\section{Reviewer \#1}

\textbf{
D1 (W1): Although VDMS mentions that it supports Visual Feature Vectors as
first class citizens in Section 3.3, the queries used in evaluation
do not include an example.
}\bigskip

Not for this work, we will add to future work.
Also, building a comparison baseline that integrates all that functionality
is very ad-hoc, and would complicate the understanding of the origins
of the benefits of VDMS.

We can provide appendix.

\bigskip
\textbf{
D2 (W1): All queries involve “resize” operation, which is expensive for the
baselines since it is happening on the client side.
A simplistic query without resizing can show how the graph model performs
against traditional RDS DBs (i.e., will show that VDMS has comparable
performance even for such use-case without "visual manipulation").
}\bigskip

This is a great point, we appreciate the suggestion.
We have added

\bigskip
\textbf{
D3 (W2): It is not clear which queries are supported or not.
The queries used for evaluation are based on tags and geo search.
What about visual-based queries? For example, is image similarity search based
on Visual Feature Vectors within a geographical region supported?
}\bigskip

VDMS do support the suggested query, i.e., perform a similarity search based
on feature vectors and also filter by geographical location.
This can be achieved using the very similar queries as the one used in
the present evaluation, plus the use of the feature vector queries,
that are natively supported using the same set of APIs.
Because of space constraints, we were not able to accommodate initial evaluation
we have been working on with Feature Vector search specifically,
and we plan to perform a more comprehensive evaluation on this functionality
of this feature because of its relevance when processing visual data, as well
as our own needs in our use cases.

\bigskip
\textbf{
D4 (W2): Section 4.3.1, paragraph 5, mentions that INTERSECTION operation is not
yet implemented at the server side.
A discussion on current limitations/future work for such queries or queries
such as in D3, will be better to be clarified in paper.
}\bigskip

Thanks for this comment, we have added a "Future Work" section where we cover
this and other question, expanding further on the most immediate lines of
improvement and research for the VDMS project.

\bigskip
\textbf{
D5 (W3): Section 4.2 paragraph 1, desing
}\bigskip

Fixed in final version.

\bigskip

\newpage
\section{Reviewer \#4}

\newpage
\section{Reviewer \#5}

\pagenumbering{arabic}

### 2021-04-28 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

Not for this work, we will add to future work.
Also, building a comparison baseline that integrates all that functionality
is very ad-hoc, and would complicate the understanding of the origins
of the benefits of VDMS.

We can provide appendix.

\bigskip
\textbf{
D2 (W1): All queries involve “resize” operation, which is expensive for the
baselines since it is happening on the client side.
A simplistic query without resizing can show how the graph model performs
against traditional RDS DBs (i.e., will show that VDMS has comparable
performance even for such use-case without "visual manipulation").
}\bigskip

This is a great point, we very much appreciate the suggestion.
We have run a new experiment and added a new figure to the paper (Figure 10),
where we compare 3 of the queries with and without the resize operation
to compare the results.
We have also added an explanation on the differences in performance
in the final version.

@@

\bigskip
\textbf{
D3 (W2): It is not clear which queries are supported or not.
The queries used for evaluation are based on tags and geo search.
What about visual-based queries? For example, is image similarity search based
on Visual Feature Vectors within a geographical region supported?
}\bigskip

VDMS does support the suggested query, i.e., perform a similarity search based
on feature vectors and also filter by geographical location.
This can be achieved using the very similar queries as the one used in
the present evaluation, plus the use of the feature vector queries,
that are natively supported using the same set of APIs.
Because of space constraints, we were not able to accommodate initial evaluation
we have been working on with Feature Vector search specifically,
and we plan to perform a more comprehensive evaluation on this functionality
of this feature because of its relevance when processing visual data, as well
as our own needs in our use cases.

@@

\bigskip
\textbf{
D4 (W2): Section 4.3.1, paragraph 5, mentions that INTERSECTION operation is not
yet implemented at the server side.
A discussion on current limitations/future work for such queries or queries
such as in D3, will be better to be clarified in paper.
}\bigskip

Thanks for this comment, we have added a "Future Work" section where we cover
this and D3, expanding further on the most immediate lines of
improvement and research for the VDMS project.

### 2021-04-28 yfcc100m/paper/vldb2021/futurework.tex
Add mention to union/intersetction operations in future work

Add future work here, responding reviewrs questions.

>>>>

Based on the results of this evaluation and our experience with VDMS
for this and other internal use cases, we have identified certain features
that are needed to fully exploit the potential of the unified back-end
for visual data infrastructure.
In particular, we have identified the urgent need for a set of UNION/INTERSECTION
interfaces to enable richer queries and improve performance,
given the limitations discussed on \ref{concurrency_analysis}.
